SEER Medicaid

### 2023-09-15 Manuscript Analysis code 0 to 19.Rmd
Minor code edits

#
table(seer0to39$SEER_DateofDeath_Year, useNA = "always")

@@

@@

# FIGURE 3 survival plots (# In_Medicaid_flag and mcont66) 
```{r}
# In_Medicaid_Flag
plot1 <- ggsurvplot(fit = survfit(Surv(fumo, can_dead) ~ In_Medicaid_Flag, data = seer0to19), 
    xlab = "Months from diagnosis", 
    ylab = "Survival probability", 
    fun="pct",  
    title = "A",
    font.title = c(12, "bold"),
    legend.title = "",
    legend = "bottom",
    font.legend=c(12, "bold"),
    legend.labs = c("Not enrolled", "Enrolled"),
    palette = c("red", "cyan3", "blue", "black"),
    font.x = c(12, "bold"),
    font.y = c(12, "bold"),
    xlim=c(0, 60),
    break.x.by = 12,
    ylim=c(50, 100),
    censor.size=0.5,
    font.tickslab = c(12, "bold"),
    pval=TRUE,
    pval.size = 5,
    pval.coord = c(2,55),
    conf.int = TRUE)

plot1

# mcont66
 plot2 <- ggsurvplot(fit = survfit(Surv(fumo, can_dead) ~ mcont66, data = seer0to19), 
    xlab = "Months from diagnosis", 
    ylab = "Survival probability", 
    fun="pct", 
    title = "B",
    font.title = c(12, "bold"),
    legend.title = "",
    legend = "bottom",
    font.legend=c(12, "bold"),
    legend.labs = c("Not enrolled", "Continuous", "Discontinuous", "Other"),
    palette = c("red", "cyan3", "blue", "black", "gray"),
    font.x = c(12, "bold"),
    font.y = c(12, "bold"),
    xlim=c(0, 60),
    break.x.by = 12,
    ylim=c(50, 100),
    censor.size=0.5,
    font.tickslab = c(12, "bold"),
    pval=TRUE,
    pval.size = 5,
    pval.coord = c(2,55),
    conf.int = TRUE)

@@

dev.off()
```
# SUPPLEMENTARY TABLE 2: Estimate survival time 0 to 19
```{r}
# In_Medicaid_Flag
SuppTable2a <- summary(survfit(Surv(fumo, can_dead) ~ In_Medicaid_Flag, data = seer0to19), times = 60) # estimates 60 month survival time
SuppTable2a <- as.data.frame(cbind(SuppTable2a$strata, round(SuppTable2a$surv*100, 2), round(SuppTable2a$lower*100, 2), round(SuppTable2a$upper*100,2))) # makes dataframe

SuppTable2a <- setNames(SuppTable2a, c("Category", "Survival Percentage", "Lower CI", "Upper CI")) # gives column names
SuppTable2a <- SuppTable2a %>%
  mutate(Category = case_when(Category ==1 ~ "Not enrolled",
                              Category ==2 ~ "Enrolled"))

#mcont66
SuppTable2b <- summary(survfit(Surv(fumo, can_dead) ~ mcont66, data = seer0to19), times = 60)
SuppTable2b <- as.data.frame(cbind(SuppTable2b$strata, round(SuppTable2b$surv*100, 2), round(SuppTable2b$lower*100, 2), round(SuppTable2b$upper*100,2)))

SuppTable2b <- setNames(SuppTable2b, c("Category", "Survival Percentage", "Lower CI", "Upper CI"))
SuppTable2b <- SuppTable2b %>%
  mutate(Category = case_when(Category ==1 ~ "Not enrolled",
                              Category ==2 ~ "Continuous",
                              Category == 3 ~ "Discontinuous",
                              Category == 4 ~ "Other"))

@@

# SUPPLEMENTARY TABLE 3: Populate a table with survival by age group
```{r}
# In_Medicaid_Flag
# calculate survival at 60 mo
results <- data.frame(matrix(ncol=5, nrow=0)) #create the table
columns<-c("Medicaid_Category", "Survival Percentage",  "LowerCI", "UpperCI", "Age_cat") #label the columns with names
colnames(results)<-columns

@@

# mcont66
# calculate survival at 60 mo
results <- data.frame(matrix(ncol=5, nrow=0)) #create the table
columns<-c("Medicaid_Category", "Survival Percentage",  "LowerCI", "UpperCI", "Age_cat") #label the columns with names
colnames(results)<-columns

@@

# SUPPLEMENTARY TABLE 4: make a function to populate a table with survival by race
```{r}
race <- unique(seer0to19$race_ethnicity)
limited <- seer0to19 %>%
 filter(race_ethnicity %in% c("Non-Hispanic White","Non-Hispanic Black",  "Non-Hispanic API", "Hispanic", "Non-Hispanic Other"))

@@

# SUPPLEMENTARY TABLE 5: make a function to populate a table with survival by tumor type
```{r}
limited <- seer0to19 %>%
 filter(can_type %in% c("I. Leukemias, myeloproliferative diseases, and myelodysplastic diseases","II. Lymphomas and reticuloendothelial neoplasms", "III. CNS and miscellaneous intracranial and intraspinal neoplasms", "IV. Neuroblastoma and other peripheral nervous cell tumors", "V. Retinoblastoma", "VI. Renal tumors", "VII. Hepatic tumors", "VIII. Malignant bone tumors", "IX. Soft tissue and other extraosseous sarcomas", "X. Germ cell tumors, trophoblastic tumors, and neoplasms of gonads", "XI. Other malignant epithelial neoplasms and malignant melanomas"))
ct<-unique(limited$can_type)

@@

# adjust for stage
res.cox2a <- coxph(Surv(fumo, can_dead) ~ In_Medicaid_Flag + race_ethnicity + age_cat + Yost_ACS_2006_2010_quintile + stage + cluster(state), data = seer0to19) # Model adjusted for race age and a measure of poverty and stagee
res.cox2a
summary(res.cox2a)

>>>>

table(seer0to39$SEER_DateofDeath_Year, useNA = "always")

table(seer0to39$can_type)

@@

table1(~age_cat + sex  + race_ethnicity + Yost_ACS_2006_2010_quintile + In_Medicaid_Flag  + stage + fumo  + can_type + can_dead2|mcont66, droplevels = TRUE, seer0to19 %>% filter(Agerecodewithsingleages_and_100 !=18 ))

table1(~mcont66|age_cat, droplevels = TRUE, seer0to19%>% filter(Agerecodewithsingleages_and_100 <18 ))
```

@@

# FIGURE 3 survival plots (# In_Medicaid_flag and mcont66) 
```{r}
# In_Medicaid_Flag
plot1 <- ggsurvplot(fit = survfit(Surv(fumo, can_dead) ~ In_Medicaid_Flag, data = seer0to19), 
    xlab = "Months from diagnosis", 
    ylab = "Survival probability", 
    fun="pct",  
    title = "A",
    font.title = c(12, "bold"),
    legend.title = "",
    legend = "bottom",
    font.legend=c(12, "bold"),
    legend.labs = c("Not enrolled", "Enrolled"),
    palette = c("red", "cyan3", "blue", "black"),
    font.x = c(12, "bold"),
    font.y = c(12, "bold"),
    xlim=c(0, 60),
    break.x.by = 12,
    ylim=c(50, 100),
    censor.size=0.5,
    font.tickslab = c(12, "bold"),
    pval=TRUE,
    pval.size = 5,
    pval.coord = c(2,55),
    conf.int = TRUE,
    hline = 90)

# plot1$plot + geom_hline(yintercept = 90)
plot1

# mcont66
 plot2 <- ggsurvplot(fit = survfit(Surv(fumo, can_dead) ~ mcont66, data = seer0to19 ), 
    xlab = "Months from diagnosis", 
    ylab = "Survival probability", 
    fun="pct", 
    title = "B",
    font.title = c(12, "bold"),
    legend.title = "",
    legend = "bottom",
    font.legend=c(12, "bold"),
    legend.labs = c("Not enrolled", "Continuous", "Discontinuous", "Other"),
    palette = c("red", "cyan3", "blue", "black", "gray"),
    font.x = c(12, "bold"),
    font.y = c(12, "bold"),
    xlim=c(0, 60),
    break.x.by = 12,
    ylim=c(50, 100),
    censor.size=0.5,
    font.tickslab = c(12, "bold"),
    pval=TRUE,
    pval.size = 5,
    pval.coord = c(2,55),
    conf.int = TRUE)

@@

dev.off()
```
# SUPPLEMENTARY TABLE 2: Estimate survival time 0 to 19 at 160 mo
```{r}
# Overall
summary(survfit(Surv(fumo, can_dead) ~ 1, data = seer0to19), times=60) # estimates 60 month survival time

# In_Medicaid_Flag
SuppTable2a <- summary(survfit(Surv(fumo, can_dead) ~ In_Medicaid_Flag, data = seer0to19), times=60) # estimates 60 month survival time

SuppTable2a <- as.data.frame(cbind(SuppTable2a$strata, SuppTable2a$time, round(SuppTable2a$surv*100, 2), round(SuppTable2a$lower*100, 2), round(SuppTable2a$upper*100,2))) # makes dataframe

SuppTable2a <- setNames(SuppTable2a, c("Category", "Time (months)", "Survival Percentage", "Lower CI", "Upper CI")) # gives column names
SuppTable2a <- SuppTable2a %>%
  mutate(Category = case_when(Category ==1 ~ "Not enrolled",
                              Category ==2 ~ "Enrolled"))

#mcont66
SuppTable2b <- summary(survfit(Surv(fumo, can_dead) ~ mcont66, data = seer0to19), times = 60)
SuppTable2b <- as.data.frame(cbind(SuppTable2b$strata, SuppTable2b$time, round(SuppTable2b$surv*100, 2), round(SuppTable2b$lower*100, 2), round(SuppTable2b$upper*100,2)))

SuppTable2b <- setNames(SuppTable2b, c("Category", "Time (months)", "Survival Percentage", "Lower CI", "Upper CI"))
SuppTable2b <- SuppTable2b %>%
  mutate(Category = case_when(Category ==1 ~ "Not enrolled",
                              Category ==2 ~ "Continuous",
                              Category == 3 ~ "Discontinuous",
                              Category == 4 ~ "Other"))

@@

# SUPPLEMENTARY TABLE 3: Populate a table with survival by age group at 60 mo
```{r}
age <- unique(seer0to19$age_cat)
# In_Medicaid_Flag
results <- data.frame(matrix(ncol=6, nrow=0)) #create the table
columns<-c("Medicaid_Category", "Time (months)", "Survival Percentage",  "LowerCI", "UpperCI", "Age_cat") # label the columns with names
colnames(results)<-columns

@@

# mcont66
# calculate survival at 60 mo
results <- data.frame(matrix(ncol=6, nrow=0)) #create the table
columns<-c("Medicaid_Category", "Time (months)","Survival Percentage",  "LowerCI", "UpperCI", "Age_cat") #label the columns with names
colnames(results)<-columns

@@

# SUPPLEMENTARY TABLE 4: Populate a table with survival by race at 60 mo
```{r}
race <- unique(seer0to19$race_ethnicity)
limited <- seer0to19 %>%
 filter(race_ethnicity %in% c("Non-Hispanic White","Non-Hispanic Black",  "Non-Hispanic API", "Hispanic", "Non-Hispanic Other"))

@@

# SUPPLEMENTARY TABLE 5: Populate a table with survival by tumor type at 12, 24, 36, 48, and 60 mo
```{r}
limited <- seer0to19 %>%
 filter(can_type %in% c("I. Leukemias, myeloproliferative diseases, and myelodysplastic diseases","II. Lymphomas and reticuloendothelial neoplasms", "III. CNS and miscellaneous intracranial and intraspinal neoplasms", "IV. Neuroblastoma and other peripheral nervous cell tumors", "V. Retinoblastoma", "VI. Renal tumors", "VII. Hepatic tumors", "VIII. Malignant bone tumors", "IX. Soft tissue and other extraosseous sarcomas", "X. Germ cell tumors, trophoblastic tumors, and neoplasms of gonads", "XI. Other malignant epithelial neoplasms and malignant melanomas"))
ct<-unique(limited$can_type)

@@

# adjust for stage
res.cox2a <- coxph(Surv(fumo, can_dead) ~ In_Medicaid_Flag + race_ethnicity + age_cat + Yost_ACS_2006_2010_quintile + stage + cluster(state), data = seer0to19) # Model adjusted for race age and a measure of poverty and stage
res.cox2a
summary(res.cox2a)
